The role of motor inhibition during covert speech production

### 2021-10-27 manuscript.tex
Minor updates in figure

Whether covert speech production is accompanied by the emission of motor commands that are subsequently inhibited has been the matter of debate \citep[e.g.,][]{geva_inner_2018}. It has been suggested that the primary motor cortex would be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018}. However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}. In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level. What cognitive and neural mechanisms operate to maintain this activity under the threshold? In this section, we provided empirical arguments in favour of the "active inhibition hypothesis". Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during inner speech production, thus preventing execution.

@@

This idea could be assessed in several ways. First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years). We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at this age. \cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old). This suggests that inhibitory control may play a peculiar role when speech is being internalised, but its role may weaken with expertise. This is consistent with results from training studies suggesting that we rely more and more on domain-general (e.g., memory-based) processes with expertise \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.

@@

The dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016} describes two neural pathways that may provide the auditory content of covert speech. First, the simulation-estimation prediction stream implements a motor-to-sensory transformation via motor simulation, that is, by simulating speech movements and the perceptual changes that would be associated with these movements \citep[see also][for a similar proposal]{loevenbruck_cognitive_2018}. This stream includes cerebral areas involved in speech motor preparation such as the supplementary motor area, the inferior frontal gyrus, the premotor cortex and the insula, as well as cerebral areas involved in somatosensory estimation and perception such as primary and secondary somatosensory regions, the parietal operculum, and the supramarginal gyrus \citep{tian_mental_2016}. Second, the memory-retrieval prediction stream may be used to provide auditory percepts by "reconstructing stored perceptual information in modality-specific cortices" \citep{tian_mental_2016}. In other words, sensory percepts would be generated by activating sensory-specific cortices from object properties stored in long-term memory. This mechanism provides sensory percepts without the need for computing the predicted sensory consequences of (non executed) motor commands. This stream includes semantic networks, including frontal, temporal, and parietal regions \citep[for more details, see][]{tian_mental_2016}.

@@

The balance between these two mechanisms (i.e., simulation vs. memory retrieval) may depend on the precise instructions given to the participants, which may clue them to produce different forms of covert speech. For instance, either one of these two streams may be recruited preferentially depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" \citep[see also the distinction between the "inner ear" and the "inner voice", e.g.,][]{smith_subvocalization_1992}. In line with this hypothesis, \cite{tian_mental_2016} have shown that inner speaking more strongly recruits cerebral regions in the simulation stream than inner hearing, which more strongly recruits cerebral regions in the memory-retrieval stream. Moreover, \cite{ma_distinct_2019} have shown that inner speaking and inner hearing have distinct MEG correlates and effects on a subsequent phonetic (discriminating /ba/ vs. /da/) categorisation task.

@@

In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost of (or equivalently, the available computational resources for) the task, which in turn determines the balance between the simulation and association mechanisms. For instance, we hypothesise that novel and/or difficult tasks (which are both computationally more expensive, ceteris paribus) may rely more on the simulation mechanism, whereas well known and/or easy tasks may rely more on associative mechanisms. This idea is supported by several studies showing a greater increase in facial EMG activity during the reading of difficult text or while performing difficult mental arithmetic tasks as compared to easier tasks \citep[e.g.,][]{faaborg-andersen_electromyography_1958, sokolov_inner_1972}, suggesting a greater involvement of the speech motor system. Alternatively, these results may suggest a lesser involvement of inhibitory mechanisms \citep[see also the discussion in][]{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}. This is congruent with the greater reliance on associative mechanisms with greater expertise, as discussed previously.

@@

Regarding the neural origin of the sensory experience of covert speech, we discussed the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, which suggests that these sensory percepts may be provided either by a motor-simulation-based process or by a memory-based process. We suggested that the balance between these two mechanisms, in addition to the task instructions which may prompt different forms of covert speech, may also be determined by the available computational resources for (or equivalently, the computational cost of) the task. More precisely, novel or more difficult tasks are expected to rely more on the motor-simulation mechanisms whereas well-known and/or easy tasks may rely more on a "memoised version" of the motor simulation: the memory-retrieval prediction stream. Whereas the former mechanism should involve active inhibitory mechanisms, the latter should not, as there should be no (or less) motor commands to inhibit. Crucially, different forms of covert speech, varying in condensation, dialogicality, or intentionality, may require inhibitory control to a different extent.

>>>>

Whether covert speech production is accompanied by the emission of motor commands that are subsequently inhibited has been the matter of debate \citep[e.g.,][]{geva_inner_2018}. It has been suggested that the primary motor cortex would be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018}. However, stating that motor imagery only involves subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}. In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level. What cognitive and neural mechanisms operate to maintain this activity under the threshold? In this section, we provided empirical arguments in favour of the "active inhibition hypothesis". Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during inner speech production, thus preventing execution.

@@

This idea could be assessed in several ways. First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years). We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at this age. \cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old). This suggests that inhibitory control may play a peculiar role when speech is being internalised, but its role may weaken with expertise. This is consistent with results from training studies suggesting that, with growing expertise, we tend to rely more and more on memory-based processes to produce mental imagery \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.

@@

The dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016} describes two neural pathways that may provide the auditory content of covert speech. First, the simulation-estimation prediction stream implements a motor-to-sensory transformation via motor simulation, that is, by simulating speech movements and the perceptual changes that would be associated with these movements \citep[see also][for a similar proposal]{loevenbruck_cognitive_2018}. This stream includes cerebral areas involved in speech motor preparation such as the supplementary motor area, the inferior frontal gyrus, the premotor cortex and the insula, as well as brain areas involved in somatosensory estimation and perception such as primary and secondary somatosensory regions, the parietal operculum, and the supramarginal gyrus \citep{tian_mental_2016}. Second, the memory-retrieval prediction stream may be used to provide auditory percepts by "reconstructing stored perceptual information in modality-specific cortices" \citep{tian_mental_2016}. In other words, sensory percepts would be generated by activating sensory-specific cortices from object properties stored in long-term memory. This mechanism provides sensory percepts without the need for computing the predicted sensory consequences of (non executed) motor commands. This stream includes semantic networks, including frontal, temporal, and parietal regions \citep[for more details, see][]{tian_mental_2016}.

@@

The balance between these two mechanisms (i.e., simulation vs. memory retrieval) may depend on the precise instructions given to the participants, which may clue them to produce different forms of covert speech. For instance, either one of these two streams may be recruited preferentially depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" \citep[see also the distinction between the "inner ear" and the "inner voice", e.g.,][]{smith_subvocalization_1992}. In line with this hypothesis, \cite{tian_mental_2016} have shown that inner speaking more strongly recruits brain regions in the simulation stream than inner hearing, which more strongly recruits brain regions in the memory-retrieval stream. Moreover, \cite{ma_distinct_2019} have shown that inner speaking and inner hearing have distinct MEG correlates and effects on a subsequent phonetic (discriminating /ba/ vs. /da/) categorisation task.

@@

In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost of (or equivalently, the available computational resources for) the task, which in turn determines the balance between the simulation and association mechanisms. For instance, we hypothesise that novel and/or difficult tasks (which are both computationally more expensive, ceteris paribus) may rely more on the simulation mechanism, whereas well known and/or easy tasks may rely more on associative mechanisms. This idea is supported by several studies showing a greater increase in facial EMG activity during the reading of difficult text or while performing difficult mental arithmetic tasks as compared to easier tasks % \citep[e.g.,][]{faaborg-andersen_electromyography_1958, sokolov_inner_1972}, suggesting a greater involvement of the speech motor system. Alternatively, these results may suggest a lesser involvement of inhibitory mechanisms \citep[see also the discussion in][]{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}. This is congruent with the greater reliance on associative mechanisms with greater expertise, as discussed previously.

@@

Regarding the neural origin of the sensory experience of covert speech, we discussed the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, which suggests that these sensory percepts may be provided either by a motor-simulation-based process or by a memory-based process. We suggested that the balance between these two mechanisms, in addition to the task instructions which may prompt different forms of covert speech, may also be determined by the available computational resources for (or equivalently, the computational cost of) the task. More precisely, novel or more difficult tasks are expected to rely more on the motor-simulation mechanisms whereas well-known and/or easy tasks may rely more on a "memoised version" of the motor simulation: the memory-retrieval prediction stream. Whereas the former mechanism should involve active inhibitory mechanisms, the latter should not, as there should be no (or less) motor commands to inhibit.

% Crucially, different forms of covert speech, varying in condensation, dialogicality, or intentionality, may require inhibitory control to a different extent.
